### 2015-04-14 dsc-shrink/investigate_cdf.rmd
fixed bug in mixfdr2fitted.g

```{r}
load("res.RData")
#load("res10.RData")
library("dscr")
library("ashr")
library(reshape2)
library(ggplot2)
library(dplyr)

#res=res10
neglong = 
  res$negprob %>% 
    select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%
    melt(id.vars=c("method","scenario","seed",".id"),value.name="negprob") %>%
    filter(negprob > 0.9)

@@

cdfplot(reslong %>% 
          filter(method %in% c("ash.n","ash.hu","ash.u","ash.hu.s") & scenario %in% c("A","B","C","efron_FCR")), "All Discoveries"
        )

>>>>

```{r}
load("res.RData")
#load("res10.RData")
#res=res10
library("dscr")
library("ashr")
library(reshape2)
library(ggplot2)
library(dplyr)

neglong = 
  res$negprob %>% 
    select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%
    melt(id.vars=c("method","scenario","seed",".id"),value.name="negprob") %>%
    filter(negprob > 0.9)

@@

cdfplot(reslong %>% 
          filter(method %in% c("ash.n","ash.hu","ash.u","ash.hu.s") & scenario %in% c("A","B","C","efron_FCR")), "All observations"
        )

### 2015-04-14 paper/main.tex
fixed bug in mixfdr2fitted.g

To illustrate this, Figure \ref{fig:egcdf} compares
the estimated $g$ from our method for each of the simulation scenarios above with the 
estimated $g$ from mixFdr which does not make the UA (and which models $g$ as a mixture of $J$ normal distributions, with $J=3$ by default).
Even with only one simulated example for each scenario, the greater reliability of estimates afforded
by the UA is immediately apparent.

@@

%deconvolution
%calculations are notoriously tricky and I have not
%been able to produce a stable general algorithm. ; see also 
Zhao+Hwang consider in detail the case where the non-null effects are normally distributed.

@@

To do: implement methods to compute posterior cdf of each observation at given points. 
Then compute these for the simulation studies. Check whether issue with upper bound is due to non-unimodal distribution.

@@

>>>>

To illustrate this, Figure \ref{fig:egcdf} compares
the estimated $g$ from our method for each of the simulation scenarios above with the 
estimated $g$ from mixFdr which does not make the UA (and which models $g$ as a mixture of $J$ normal distributions, with $J=3$ by default).
Even with only one simulated example for each scenario, the greater reliability of estimates afforded
by the UA is immediately apparent. In particular the greater tendency for mixFdr to overestimate $\pi_0$ is readily visible in its behaviour at 0.
And the estimated cdf from mixFdr often has a vertical (or almost vertical)
segment at some non-zero location, indicative of a concentration of density in the estimated $g$ at that location. This corresponds to
one of the 3 mixture components being estimated to be centered at that location with very small variance. 
The UA prevents this kind of ``irregular" behaviour, effectively requiring $g$ to be somewhat smooth.
While the UA is not the only way to achieve this, it is a simple and effective approach.

Interestingly, even in the ``bimodal" scenario where the UA is severely contradicted, the estimated $g$ from $\ashr$ 
is visually more accurate than that from mixFdr: although mixFdr is capable, in principle, of fitting the multiple modes of $g$, it does not do this well here. We believe this
is mostly because the noise level is sufficiently large to make reliable estimation of the multiple modes difficult, rather than reflecting
deficiencies in the specific choices made by mixFdr, and indeed in simulations where the modes are sufficiently well-spaced
to be clearly visible in the observed $\betahat$, mixFdr is able to fit this modes (Supplementary Information; 
\url{dsc-shrink/check_mixfdr_lownoise.rmd}). Of course, we would not advocate the UA in settings where multi-modality is 
clearly visible in the observed $\betahat$.

@@

\subsubsection*{Reliable estimates of $g$ lead to reasonable coverage behaviour}

Coverage rates are given in:
\url{file:///Users/stephens/Dropbox/Documents/git/ash/dsc-shrink/investigate_cdf.html}

Zhao+Hwang consider in detail the case where the non-null effects are normally distributed.

@@

@@

Notes from Adrian Raftery -

Newcombe reference (1880s?)
Dean and Raftery
Uniform is super-efficient
